### 2019-07-08 1-Preamble/4-Acknowledgement/acknowledgement.tex
Je vais au bureau, une dernière relecture de résumé / intro fr / intro anglais / conclusion et ça ira

Of course on a more personal level, my thoughts are strongly dedicated to my family.
%
I first want to thank my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian}, who has always been my main model and who has been of a constant support during all my life and in my studies.
His rigour, dedication and seriousness kept pushing me further, and I am immensely proud of him.
Some of our board game nights were brain teasers comparable with some maths problems solved for this thesis!
% and I was happy to help him for the organization of the \href{http://lettres.sorbonne-universite.fr/Kaamelott}{research colloque}\footnote{~Un livre a aussi été publié suite \href{http://lettres.sorbonne-universite.fr/Kaamelott}{au colloque}, \href{https://www.editions-vendemiaire.com/catalogue/a-paraitre/kaamelott-un-livre-d-histoire-florian-besson-et-justine-breton-dir/}{``Kaamelott, un livre d'histoire'', aux éditions Vandémiaire}.} on the \emph{Kaamelott} french TV show in February 2017, it was \href{https://www.fabula.org/actualites/kaamelott-ou-la-relecture-de-l-histoire_75490.php}{the funniest} and \href{https://www.vousnousils.fr/2017/03/22/kaamelott-un-tremplin-vers-lhistoire-et-la-litterature-601428}{most exciting} \href{https://lpcm.hypotheses.org/10718}{research event} I have been to in the last four years!
%
I also thank my younger brother Fabian, for being an inspiration for other (highly important) directions of my life. \emph{Ton courage et ta force m'inspirent quotidiennement, merci beaucoup !}
Very warm thanks then go to M. and my grand-parents, J. \& J.-M. and J., and to my uncle J. and aunt B.!
Finally, I thank sincerely my parents, C. and P., for being the best parents since the last $26$ years, and for their (vital) moral support.
\emph{Merci infiniment de nous avoir offert cette curiosité, merci d'être si gentils, et merci de votre soutien constant et de votre amour !}
\\
\indent
I would then like to thank my closest friends, sorted in chronological order of our first encounter in the \href{https://bulbapedia.bulbagarden.net/wiki/Tall_grass}{tall grass}\footnote{~Sorry if I forgot you, it's much harder to keep track of wild encounters in the tall grass in real wife, without a Pokédex! And due to space constraints, I had to choose quite arbitrarily whom to include\dots}: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia and Julia in Briançon, Mayotte and Pierre in Marseille, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément in Cachan, Jill-Jênn, Alain, Claire, Édouard, Loïc and Damien also in Cachan, Kumudham in India, Thibault, Sébastien, Sélim, Valentin again in Cachan, and Audrey, Rémi, Marine, Adrien, Bastien, Claire, Corentin and Lola in Rennes.
% In the last four years, thank you so much my dear friends, for great moments and an even greater moral support, for the holidays in India, Switzerland, Hungary/Austria, Strasbourg, Greece, Saint-Malo, Normandy, Scotland, Marseille, Madrid, Brittany etc. I loved traveling with you and hope to continue!
\emph{Une pensée particulière pour Hélène, merci pour ton énergie et ta détermination depuis 2018.}

@@

During my PhD, I was lucky to teach regularly in Mathematics and Computer Science.
I warmly thank David Pichardie for his trust and support, and also François Schwarzentruber, Nathalie Bertrand and David Cachera at ENS de Rennes, and Romaric Gaudel and his colleagues at ENSAI. Thanks to them, I loved to teach these $3 \times 64$ hours.
% since October $2016$.
% I am trully honored to join \emph{the Département d'Informatique} at ENS de Rennes in next September $2019$.
Thanks to my amazing students, I am proud of you and of our interesting exchanges.
%  and I feel lucky to be able to keep working alongside some of you.
I am thankful to Amélie Stainer and Gilbert Gabillard at Lycée Chateaubriand and Joliot-Curie for useful discussions.
\\
\indent
I am grateful to all the amazing professors who shared their passion for mathematics and computer science with me.
A partial list includes Hubert P. in Briançon ($2006$-$09$), Yassine D. ($2009$-$10$) and Agnès B. ($2010$-$11$) in Lycée Thiers, Marseille.
Then at ENS de Cachan ($2011$-$16$), I especially think about Frédéric P., Alain T., Claudine P., Florian de V. and Nicolas V. in Maths, to Hubert C.-L., Jean G.-L., Sylvain S., Paul G., Serge H. in Computer Science, and to Carine S.-P., Delphine L. and the late Nicolas P.\textsuperscript{$\dagger$} for their support.
I also thank Didier C., Vijaysekhar C. and Jai P. in Hyderabad ($2014$-$15$), Michael U. and Julien F. in Lausanne ($2016$).

>>>>

Of course on a more personal level, my thoughts are strongly dedicated to my family.
%
I first want to thank my \href{https://paris-sorbonne.academia.edu/FBesson}{older brother Florian}, who has always been my main model and who has been of a constant support during all my life and in my studies.
His rigour, dedication and seriousness kept pushing me further, and I am immensely proud of him.
Some of our board game nights were brain teasers comparable with some maths problems solved for this thesis!
% and I was happy to help him for the organization of the \href{http://lettres.sorbonne-universite.fr/Kaamelott}{research colloque}\footnote{~Un livre a aussi été publié suite \href{http://lettres.sorbonne-universite.fr/Kaamelott}{au colloque}, \href{https://www.editions-vendemiaire.com/catalogue/a-paraitre/kaamelott-un-livre-d-histoire-florian-besson-et-justine-breton-dir/}{``Kaamelott, un livre d'histoire'', aux éditions Vandémiaire}.} on the \emph{Kaamelott} french TV show in February 2017, it was \href{https://www.fabula.org/actualites/kaamelott-ou-la-relecture-de-l-histoire_75490.php}{the funniest} and \href{https://www.vousnousils.fr/2017/03/22/kaamelott-un-tremplin-vers-lhistoire-et-la-litterature-601428}{most exciting} \href{https://lpcm.hypotheses.org/10718}{research event} I have been to in the last four years!
%
I also thank my younger brother Fabian, for being an inspiration for other (highly important) directions of my life. \emph{Ton courage et ta force m'inspirent quotidiennement, merci beaucoup !}
Very warm thanks then go to M. and my grand-parents, J. \& J.-M. and J., and to my uncle J. and aunt B.!
Finally, I thank sincerely my parents, C. and P., for being the best parents since the last $26$ years, and for their (vital) moral support.
\emph{Merci infiniment de nous avoir offert cette curiosité, merci d'être si gentils, et merci de votre soutien constant et de votre amour !}
% \\
% \indent

I would then like to thank my closest friends, sorted in chronological order of our first encounter in the \href{https://bulbapedia.bulbagarden.net/wiki/Tall_grass}{tall grass}\footnote{~Sorry if I forgot you, it's harder to keep track of wild encounters in the tall grass without a Pokédex!}: Guillaume, Florian, Marian, Hélène, Lucie, Lætitia and Julia in Briançon, Mayotte and Pierre in Marseille, Laurent, Simon, Tristan, Ludovic, Jessica, Romain, Benjamin, Angèle, Clément in Cachan, Jill-Jênn, Alain, Claire, Édouard, Loïc and Damien also in Cachan, Kumudham in India, Thibault, Sébastien, Sélim, Valentin again in Cachan, and Audrey, Rémi, Marine, Adrien, Bastien, Claire, Corentin and Lola in Rennes.
%  And due to space constraints, I had to choose quite arbitrarily whom to include\dots
% In the last four years, thank you so much my dear friends, for great moments and an even greater moral support, for the holidays in India, Switzerland, Hungary/Austria, Strasbourg, Greece, Saint-Malo, Normandy, Scotland, Marseille, Madrid, Brittany etc. I loved traveling with you and hope to continue!
\emph{J'ai une pensée particulière pour Hélène, merci pour ton énergie et ta détermination, notamment en 2018-19.}

@@

During my PhD, I was lucky to teach regularly in Mathematics and Computer Science.
I warmly thank David Pichardie for his trust and support, and also François Schwarzentruber, Nathalie Bertrand and David Cachera at ENS de Rennes, and Romaric Gaudel and his colleagues at ENSAI. Thanks to them, I loved to teach these $3 \times 64$ hours.
% since October $2016$.
% I am trully honored to join \emph{the Département d'Informatique} at ENS de Rennes in next September $2019$.
Thanks to my amazing students, I am proud of you and of our interesting exchanges.
%  and I feel lucky to be able to keep working alongside some of you.
I am thankful to Amélie Stainer and Gilbert Gabillard at Lycée Chateaubriand and Joliot-Curie for useful discussions.
\\
\indent
I am grateful to amazing professors who passed on their passion for mathematics and computer science to me.
A partial list includes Hubert P. in Briançon ($2006$-$09$), Yassine D. ($2009$-$10$) and Agnès B. ($2010$-$11$) in Lycée Thiers, Marseille.
Then at ENS de Cachan ($2011$-$16$), I especially think about Frédéric P., Alain T., Claudine P., Florian de V. and Nicolas V. in Maths, to Hubert C.-L., Jean G.-L., Sylvain S., Paul G., Serge H. in Computer Science, and to Carine S.-P., Delphine L. and Nicolas P.\textsuperscript{$\dagger$} for their support.
Thanks to Didier C. and Vijaysekhar C. in Hyderabad ($2014$-$15$), Michael U. and Julien F. in Lausanne ($2016$) for our collaborations.
